Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-30 docs/ms.tex
Update ms.tex

In summary,We have presented a conceptually simple method for estimating tangential shear ,
with carefully calculated uncertainty estimates. This method is intrinsically cope with high noise levels on the input data and naturally
allows bad fit to be identified from the residuals map.
We have proposed an exceeding flexible model for intrinsic shape distribution allows us to obtain the correct posterior distributions,
while avoiding making unsupported assumptions.

>>>>

In summary,We have presented a conceptually simple method for estimating tangential shear ,
with carefully calculated uncertainty estimates. This method is intrinsically cope with high noise levels on the input data and naturally
allows bad fit to be identified from the residuals map.
We have proposed an exceeding flexible model for intrinsic shape distribution allows us to obtain the correct posterior distributions,
while avoiding making unsupported assumptions.The Gibbs sampler allows us to sample the posterior distribution of shear in 
large number of sky patches simultaneously and efficiently.
